---
title: "Interactive GeoLibre map"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

This page runs the same `geolibre` code used in RStudio, Quarto, R Markdown,
and Shiny. The widgets below embed the hosted GeoLibre application, so viewing
the live maps requires JavaScript and internet access.

```{r library}
library(geolibre)
```

## Load a GeoLibre project

A complete `.geolibre.json` project can be loaded from a URL and passed to
`geolibre()`. This example opens a 3D map of New York City buildings and subway
lines. The project is fetched while this page is built, so the chunk reports the
error rather than failing the build if the host is unreachable.

```{r nyc-buildings, error=TRUE}
project_url <- "https://assets.geolibre.app/projects/nyc-buildings.geolibre.json"
nyc_buildings <- jsonlite::read_json(project_url, simplifyVector = FALSE)

geolibre(nyc_buildings, panels = "collapsed")
```

## A single point

Style overrides can be passed as named arguments or through a `style` list.

```{r interactive-map}
point <- list(
  type = "Feature",
  properties = list(name = "Washington, DC"),
  geometry = list(
    type = "Point",
    coordinates = c(-77.0369, 38.9072)
  )
)

geolibre(layout = "maponly", height = 600) |>
  add_geojson(point, name = "Washington, DC", fillColor = "#dc2626", circleRadius = 8) |>
  set_view(center = c(-77.0369, 38.9072), zoom = 10)
```

## Points from a data frame

`add_xy_data()` reads longitude and latitude columns and keeps the remaining
columns as feature properties, so they appear when a point is clicked.
`fit_bounds()` frames the result.

```{r cities}
cities <- data.frame(
  name = c("Washington", "New York", "Boston", "Philadelphia"),
  population = c(689545, 8336817, 654776, 1603797),
  longitude = c(-77.0369, -74.0060, -71.0589, -75.1652),
  latitude = c(38.9072, 40.7128, 42.3601, 39.9526)
)

geolibre(layout = "maponly", height = 600, basemap = "positron") |>
  add_circle_markers(cities, name = "Cities", radius = 9, fillColor = "#2563eb") |>
  fit_bounds(c(-78, 38, -70, 43))
```

## A choropleth with a legend

`add_choropleth()` classifies a numeric column and colors it from a named ramp,
computing the same graduated stops the application's Style panel produces.
`color_ramp_names()` lists the ramps, and `interpolate_ramp_colors()` samples one
so a legend can match the map.

```{r ramps}
color_ramp_names()
```

```{r choropleth}
counties <- list(
  type = "FeatureCollection",
  features = list(
    list(
      type = "Feature",
      properties = list(name = "Low", value = 10),
      geometry = list(type = "Point", coordinates = c(-77.5, 38.5))
    ),
    list(
      type = "Feature",
      properties = list(name = "Middle", value = 55),
      geometry = list(type = "Point", coordinates = c(-77.0, 39.0))
    ),
    list(
      type = "Feature",
      properties = list(name = "High", value = 100),
      geometry = list(type = "Point", coordinates = c(-76.5, 39.5))
    )
  )
)

breaks <- interpolate_ramp_colors("blues", 3)

geolibre(layout = "maponly", height = 600) |>
  add_choropleth(
    counties,
    column = "value",
    name = "Observations",
    colormap = "blues",
    class_count = 3,
    circleRadius = 14
  ) |>
  add_legend(
    "Observations",
    labels = c("10", "55", "100"),
    colors = breaks,
    shape = "circle"
  ) |>
  set_view(center = c(-77, 39), zoom = 8)
```

## Rasters and a colorbar

A remote Cloud Optimized GeoTIFF is read directly by the browser, so the server
must support CORS and HTTP range requests. `add_colorbar()` labels a single-band
raster's value range.

```{r raster, eval=FALSE}
geolibre(layout = "maponly", height = 600) |>
  add_raster(
    "https://opendata.digitalglobe.com/events/california-fire-2020/pre-event/2018-02-16/pine-gulch-fire20/1030010076004E00.tif",
    name = "Imagery",
    bands = c(1, 2, 3)
  ) |>
  add_colorbar(colormap = "terrain", vmin = 0, vmax = 3000, label = "Elevation", units = "m")
```

## Inspecting and rearranging layers

Every layer function addresses a layer by its name or its id. `get_layers()`
returns one row per layer.

```{r layers}
map <- geolibre() |>
  add_marker(-77.0369, 38.9072, name = "Capital") |>
  add_tile_layer("https://tile.openstreetmap.org/{z}/{x}/{y}.png", name = "OpenStreetMap")

get_layers(map)

map <- map |>
  move_layer("OpenStreetMap", 1) |>
  set_layer_opacity("OpenStreetMap", 0.5)

layer_names(map)
```

`describe_project()` summarizes a project without printing its inlined data.

```{r describe}
summary <- describe_project(map)
summary$layerCount
summary$mapView$zoom
```

## Saving and exporting

A project saves to GeoLibre's portable `.geolibre.json` format, which the web
app, the desktop app, and the Python API all read. `to_html()` writes a
standalone page that needs no running R session.

```{r project-files}
path <- file.path(tempdir(), "example.geolibre.json")
save_project(map, path)

restored <- geolibre(load_project(path))
layer_names(restored)
```

```{r html-export}
html_path <- file.path(tempdir(), "example.html")
to_html(map, html_path, title = "Example map")
file.exists(html_path)
```

If the embedded application is unavailable, open
[GeoLibre Web](https://web.geolibre.app/) directly.
